Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-01 paper.tex
01.01.2016 (2)

To investigate the question, whether we can build practical tools from the
the symbolic execution engine, we re-implemented the engine with the specifications
of the previous symbolic execution semantics
\cite{Nguyen:2014:BCG:2635868.2635928} for PHP and additional features, such as
object-oriented programming, and extensive array support. We evaluated our
symbolic execution engine for large-scale and modern PHP systems.

During introduction of new semantics for object-orientation we encountered two main challenges. 
First, we walked a boundary between a purely symbolic or mixed concrete and symbolic execution engine
since concrete execution, e.g. foreach loops for arrays, increased code
coverage significantly. Second, we had to make a trade-off between the accuracy
of method calls and the scalability of this language feature as a method call
for different program state variants can have multiple targets.

>>>>

To investigate the question, whether we can build practical tools from the
the symbolic execution engine, we re-implemented the engine with the specifications
of the previous symbolic execution semantics
\cite{Nguyen:2014:BCG:2635868.2635928} for PHP and additional features, such as
object-oriented programming. We evaluated our
symbolic execution engine for large-scale and modern PHP systems.

During introduction of new semantics for object-orientation we encountered two main challenges. 
First, we were bound to introduce more concrete execution features to the symbolic execution engine, e.g. foreach loops for arrays, as this increased code coverage significantly. Second, we had to make a trade-off between the accuracy
of method calls and the scalability of this language feature as a method call
for different program state variants can have multiple targets.
